\section{Introduction}

\textit{Motivation for the problem tackled in the project and the background literature should be given here.}

\textit{ The first part of the introduction is composed of four main paragraphs (you can also divide them into more paragraphs) -- do not add titles, the titles are just for your reference to understand the context:}

\begin{enumerate}
    \item \textit{The Hook: What the domain is and why it is important. What is the overall problem or situation in that domain?}
    
    \item \textit{The Gap: What are the conclusions of existing literature for that problem/situation in this domain? What is the problem or issue with that existing literature?}
    
    \item \textit{The Study: Indicate how this study addresses that problem or issue (Must start with ``In this project, we...''). Describe the study, sample, and method for addressing that problem or issue}
    
    \item \textit{Contribution: Describe what you found. State explicitly how these findings extend and contribute to existing knowledge OR how and why your project classifies as a complete product.}
\end{enumerate}



\subsection{Literature Survey}
\textit{Integrate your literature survey here, indicating gaps in existing literature and how your project addresses them. \cite{dummy_ref}.} 

\subsection{Aim and Research Questions}
\textit{Provide the main objectives of the project, including the research questions you are proposing to answer and your hypotheses. If your work is not research-based, explicitly describe what your product offers in terms of innovation (still with questions, hypotheses, and validation). }
